Hierarchy Builder

### 2020-04-27 coqws/easychair.tex
link the github

The details of \HB{}, including its compilation to the (Flat) Packed Classes
discipline and its implementation in the Elpi extension language for Coq,
are given in~\cite{cohen:hal-02478907}.
In this talk we focus on how to use \HB{} in a Coq development, and we plan
to not detail how it works behind the scenes, unless specific questions
arise from the audience.

>>>>

The details of \HB{}, including its compilation to the (Flat) Packed Classes
discipline and its implementation in the Elpi extension language for Coq,
are given in~\cite{cohen:hal-02478907}.
In this talk we focus on how to use \HB{} in a Coq development,
% and we plan to not detail how it works behind the scenes, 
unless questions on its internals arise from the audience.\\
\HB{} is available for download at \url{https://github.com/math-comp/hierarchy-builder}
